Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/eval.tex
Commit
Fixed citations

\subsubsection{ZIP Files.}
\input{fig-zip}
\label{s:eval-format-zip}
Another particularly tricky file format is the ZIP compressed archive format\cite{pkzip}.
ZIP files are normally parsed end-to-beginning. At the end of each ZIP file is an \emph{end-of-directory
header}. This header contains a variable length comment, so it has to be located by scanning
backwards from the end of the file until a magic number and a valid length field is found. Many ZIP
implementations disagree on how to find this header in confusing situations, such as when the
comment contains the valid magic bytes\cite{wolf-berlinsides-zip}.
This end-of-directory header contains the offset and size of the \emph{ZIP directory}, which is an
array of one \emph{directory entry header} per file in the archive.
Each entry stores file meta data, such as file name, compressed and uncompressed size and a checksum,
in addition to the offset of a \emph{local file header}. The local file header duplicates most
information from the directory entry header and the compressed file contents follow it immediately.

@@

\noindent\begin{tabular}{@{}lll@{}} 
\toprule
\textbf{System} & \textbf{Nail LoC}  & \textbf{LoC w/o Nail} \\
\midrule
DNS server & 295 & 683 (Hammer parser)\\
&&  ~10.000 (DJBDNS)\\ 
DNS \texttt{host} tool & 210  & \XXX[TODO]\\
\texttt{unzip} & 220 & 1600 (Info-Zip) \\
\bottomrule
\end{tabular}
%%DNS: 
\paragraph{DNS.}

@@

The Hammer parser framework\cite{hammer-dns} ships with a toy DNS server that responds to
any valid DNS query with a CNAME record to the domain ``spargelze.it''. 
The server consists of 683 lines of C, mostly custom validators, semantic actions,
and data structure definitions, with only 52 lines of code defining the
grammar with Hammer's combinators.

@@

We compare the performance of our DNS server to the release 9.9.5 of ISC BIND 9\cite{bind8}, one of
the oldest and most popular DNS daemons, on a load that resembles the authoritative name server at a
hosting company. First, we generated domain names consisting of one or
two labels randomly selected from an English dictionary and one label that is one of three popular
Top Level Domains: ``com'', ``net'' or ``org''. Second, we randomly selected 90\% of these domains and
created a zone file that mapped these domain names to the local IP address.

>>>>

\subsubsection{ZIP Files.}
\input{fig-zip}
\label{s:eval-format-zip}
Another particularly tricky file format is the ZIP compressed archive format\cite{pkzip}.
ZIP files are normally parsed end-to-beginning. At the end of each ZIP file is an \emph{end-of-directory
header}. This header contains a variable length comment, so it has to be located by scanning
backwards from the end of the file until a magic number and a valid length field is found. Many ZIP
implementations disagree on how to find this header in confusing situations, such as when the
comment contains the valid magic bytes\cite{wolf:berlinsides-zip}.
This end-of-directory header contains the offset and size of the \emph{ZIP directory}, which is an
array of one \emph{directory entry header} per file in the archive.
Each entry stores file meta data, such as file name, compressed and uncompressed size and a checksum,
in addition to the offset of a \emph{local file header}. The local file header duplicates most
information from the directory entry header and the compressed file contents follow it immediately.

@@

\noindent\begin{tabular}{@{}lll@{}} 
\toprule
\textbf{System} & \textbf{Nail LoC}  & \textbf{LoC w/o Nail} \\
\midrule
DNS server & 295 & 683 (Hammer parser)\\
&&  ~10.000 (DJBDNS)\\ 
DNS client & 210  & 4,615 (host) \\
\texttt{unzip} & 220 & 1600 (Info-Zip) \\
\bottomrule
\end{tabular}
%%DNS: 
\paragraph{DNS.}

@@

The Hammer parser framework\cite{hammer-parser} ships with a toy DNS server that responds to
any valid DNS query with a CNAME record to the domain ``spargelze.it''. 
The server consists of 683 lines of C, mostly custom validators, semantic actions,
and data structure definitions, with only 52 lines of code defining the
grammar with Hammer's combinators.

@@

We compare the performance of our DNS server to the release 9.9.5 of ISC BIND 9\cite{bind9}, one of
the oldest and most popular DNS daemons, on a load that resembles the authoritative name server at a
hosting company. First, we generated domain names consisting of one or
two labels randomly selected from an English dictionary and one label that is one of three popular
Top Level Domains: ``com'', ``net'' or ``org''. Second, we randomly selected 90\% of these domains and
created a zone file that mapped these domain names to the local IP address.

### 2014-05-01 paper/osdi14/relwk.tex
Fixed citations

\XXX[https://github.com/qualiancy/lotus also supports arbitrary formats,
     but requires explicit encode/decode rules.  actually kind-of like
     pack/unpack.]

@@

>>>>

@@

Parsifal~\cite{ANSSI:parsifal} is a parser framework that also supports generating output for Ocaml.
Parsifal structures grammars as an Ocaml type that holds an internal model and functions for parsing
input and output.
However, their generator can only produce parsers and generators for simple, fixed-size structures.
The programmer can then use these when implementing parsers and generators for more
complicated formats, manually handling offsets, checksums and the like, risking bugs. Nail can
handle more complicated constructs without the programmer writing code to support them.
